Social QA Credibility Study
========================================================

``` {r loading, include=FALSE, cache=FALSE}
require(ProjectTemplate)
setwd("..")
load.project()
```

### Summary of study participants
``` {r participants, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pt.table <- xtable(table.participants())
print(pt.table, type="html")
```

### Correlations
Table: Correlation betwen user credibility rating and community score, by test group
``` {r correlation1, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
cor1.table <- xtable(cor.score())
print(cor1.table, type="html")
```

Table: Correlation between user credibility rating and answerer's reputation, by test group
``` {r correlation2, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
cor2.table <- xtable(cor.rep())
print(cor2.table, type="html")
```

Table: Correlation between user credibility rating and answerer's reputation, by prior knowledge
``` {r correlation3, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
cor2.table <- xtable(cor.priork.score())
print(cor2.table, type="html")
```

Table: Correlation between user credibility rating and answerer's reputation, by prior knowledge
``` {r correlation4, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
cor2.table <- xtable(cor.priork.rep())
print(cor2.table, type="html")
```

Figure: Prior knowledge and confidence
```{r priork, echo=FALSE, fig.width=7, fig.height=6}
priork.graph()
```

### Comment classification according to persuasiveness score - UG
``` {r comments1,echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pers.table <- xtable(table.coding.persuasiveness(rbind(df.ug.rep, df.ug.norep)))
print(pers.table, type="html")
```

### Comment classification according to persuasiveness score - PG
``` {r comments2,echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pers.table <- xtable(table.coding.persuasiveness(rbind(df.msc.rep, df.msc.norep)))
print(pers.table, type="html")
```

### Comment classification according to persuasiveness score - Phil
``` {r comments3,echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pers.table <- xtable(table.coding.persuasiveness(rbind(df.phil.rep, df.phil.norep)))
print(pers.table, type="html")




