Social QA Credibility Study
========================================================

``` {r loading, include=FALSE, cache=FALSE}
require(ProjectTemplate)
setwd("..")
load.project()
```

### Summary of study participants
``` {r participants, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pt.table <- xtable(df.participants)
print(pt.table, type="html")
```

### Correlations
Table: Correlation betwen user credibility rating and community score
``` {r correlation1, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
cor1.table <- xtable(cor.score())
print(cor1.table, type="html")
```

Table: Correlation between user credibility rating and answerer's reputation
``` {r correlation2, echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
cor2.table <- xtable(cor.rep())
print(cor2.table, type="html")
```

Figure: Prior knowledge and confidence
```{r priork, echo=FALSE, fig.width=7, fig.height=6}
priork.graph()
```

### Comment classification according to persuasiveness score
``` {r comments1,echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pers.table <- xtable(df.bp.cols)
print(pers.table, type="html")
```

### Comment classification according to prior knowledge score
``` {r comments2,echo=FALSE, message=FALSE, results='asis', prompt=FALSE}
pk.table <- xtable(df.pk.cols)
print(pk.table, type="html")
```


